---
title: "Aesthetic themes, scales and color palettes for using with `ggplot2` plots"
author: "Daniel Marcelino <<dmarcelino@live.com>>"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
    number_sections: true
create_dir: false
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  sanitize=TRUE
)
# <meta
#  http-equiv="refresh"
#  content="0; URL='http://danielmarcelino.github.io/SciencesPo/ggplot2_themes.html'"
#/>
```


The R package `ggdecor` provides a collection of functions for analyzing elections and political behavior data, including measures of political fragmentation, seat apportionment, visualization aesthetic styles.


Core themes:

* `set_urbn_defaults()`
* `theme_urbn_print()`
* `theme_urbn_map()`

Formatting functions:

* `urbn_logo_text()`
* `remove_ticks()`
* `remove_axis()`
* `scatter_grid()`
* `add_axis()`
* `urbn_geofacet`

Utility functions:

* `lato_test()`
* `lato_install()`
* `fontawesome_test()`
* `fontawesome_install()`
* `view_palette()`


# Themes
## Theme for publications (`theme_scpo`)

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
 library(ggplot2)
 library(ggdecor)
 library(dplyr)


 ggplot(mtcars, aes(mpg, wt)) +
 geom_point() +
 labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 scatterplot example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
   theme_web()
```



```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
#' # seminal bar chart#'
 count(mpg, class) %>%
   ggplot(aes(class, n)) +
   geom_col() +
   geom_text(aes(label=n), nudge_y=3) +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_web(grid="Y")
```

## Theme with roboto (`theme_roboto`)

```{r,fig.show='hold', fig.width = 6, fig.height = 4.5}

 ggplot(mtcars, aes(mpg, wt)) +
 geom_point() +
 labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 scatterplot example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
   theme_roboto()
```



```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
#' # seminal bar chart#'
 count(mpg, class) %>%
   ggplot(aes(class, n)) +
   geom_col() +
   geom_text(aes(label=n), nudge_y=3) +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_roboto(grid="Y")
```




## Theme with public sans (`theme_sans`)

```{r, fig.show='hold',  fig.width = 6, fig.height = 4.5}


 ggplot(mtcars, aes(mpg, wt)) +
 geom_point() +
 labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 scatterplot example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
   theme_sans()
```



```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
#' # seminal bar chart#'
 count(mpg, class) %>%
   ggplot(aes(class, n)) +
   geom_col() +
   geom_text(aes(label=n), nudge_y=3) +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_sans(grid="Y")
```




## Theme with xkcd font (`theme_xkcd`)

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}


 ggplot(mtcars, aes(mpg, wt)) +
 geom_point() +
 labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 scatterplot example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
   theme_xkcd()
```



```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
#' # seminal bar chart#'
 count(mpg, class) %>%
   ggplot(aes(class, n)) +
   geom_col() +
   geom_text(aes(label=n), nudge_y=3) +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_xkcd(grid="Y")
```



## Theme nero (`theme_nero`)

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}

 ggplot(mtcars, aes(mpg, wt)) +
 geom_point(color = "tomato") +
 labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 scatterplot example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
   theme_nero()
```



```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
#' # seminal bar chart#'
 count(mpg, class) %>%
   ggplot(aes(class, n)) +
   geom_col() +
   geom_text(aes(label=n), nudge_y=3) +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_nero(grid="Y")
```



## Theme Edward Tufte (`theme_nero`)

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}

p <- ggplot(mtcars, aes(mpg, wt)) +
 geom_point(color = "tomato") +
#  scale_y_continuous(breaks = extended_range_breaks()(mtcars$wt)) +
#  scale_x_continuous(breaks = extended_range_breaks()(mtcars$mpg)) +
 labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 scatterplot example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") 

# p + geom_rangeframe() +
#  theme_tufte()

p + geom_rug() +
 theme_tufte(ticks = FALSE)
```


p <- ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  scale_x_continuous(breaks = extended_range_breaks()(mtcars$wt)) +
  scale_y_continuous(breaks = extended_range_breaks()(mtcars$mpg)) +
  ggtitle("Cars")


 

# Scales (Axis)

## Percent

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
#' # seminal bar chart#'
 count(mpg, class) %>%
  mutate(pct=n/sum(n)) %>% 
   ggplot(aes(class, pct)) +
   geom_col() +
  scale_y_percent() +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_web(grid="Y")
```



## Comma

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}

#' # seminal bar chart#'
 count(mpg, class) %>%
  mutate(n=n*2000) %>% 
  arrange(n) %>% 
  mutate(class=factor(class, levels=class)) %>% 
  ggplot(aes(class, n)) +
   geom_col() +
   geom_text(aes(label=scales::comma(n)), hjust=0, nudge_y=2000) +
  scale_y_comma(limits=c(0,150000)) +
  coord_flip() +
   labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
        title="Seminal ggplot2 bar chart example",
        subtitle="A plot that is only useful for demonstration purposes",
        caption="Brought to you by 'ggplot2'") +
     theme(axis.text.y=element_blank()) +
   theme_web(grid="X")
```


## Branding

```{r example2}
library(ggplot2)
library(ggdecor)
library(grid)
library(gridExtra)

```



# Scales (Color palettes)

## SciencesPo palette

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(scpo_palette()(12))
```

## Classic 20 tons

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(classic()(20))
```



## Tableau palette

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(tableau20()(20))
```


```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
show_col(tableau10()(10))
```


```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}

show_col(tableau10_light()(10))
```


```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
show_col(tableau10_medium()(10))
```


## Theme web 10 and 20 tons

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(web10()(10))


show_col(web20()(20))


show_col(web20b()(20))


show_col(web20c()(20))
```




## Theme labs 16 and 20 tons

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(labs16()(16))


show_col(labs22()(22))

```





## Theme labs redfocus, greenfocus, and bluefocus

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(redfocus()(10))


show_col(greenfocus()(10))


show_col(bluefocus()(10))
```




## Theme labs rainbow 6, 8, 10, and 12,

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(rainbow6()(10))



show_col(rainbow8()(10))


show_col(rainbow10()(10))


show_col(rainbow12()(12))
```




## Theme labs rich 6, 8, 10, and 12,

```{r, fig.show='hold', fig.width = 6, fig.height = 4.5}
library(ggplot2)
library(scales)

show_col(rich6()(10))



show_col(rich8()(10))


show_col(rich10()(10))


show_col(rich12()(12))
```



```{r, eval=FALSE}

name           value
<chr>          <chr>
  1 Black          #000000
2 Orange         #E69F00
3 Sky Blue       #56B4E9
4 Bluish Green   #009E73
5 Yellow         #F0E442
6 Blue           #0072B2
7 Vermillion     #D55E00
8 Reddish Purple #CC79A7


ggthemes_data$few
$colors
$colors$Light
# A tibble: 9 x 2
name   value
<chr>  <chr>
  1 Gray   #8C8C8C
2 Blue   #88BDE6
3 Orange #FBB258
4 Green  #90CD97
5 Pink   #F6AAC9
6 Brown  #BFA554
7 Purple #BC99C7
8 Yellow #EDDD46
9 Red    #F07E6E

$colors$Medium
# A tibble: 9 x 2
name   value
<chr>  <chr>
  1 Gray   #4D4D4D
2 Blue   #5DA5DA
3 Orange #FAA43A
4 Green  #60BD68
5 Pink   #F17CB0
6 Brown  #B2912F
7 Purple #B276B2
8 Yellow #DECF3F
9 Red    #F15854

$colors$Dark
# A tibble: 9 x 2
name   value
<chr>  <chr>
  1 Gray   #000000
2 Blue   #265DAB
3 Orange #DF5C24
4 Green  #059748
5 Pink   #E5126F
6 Brown  #9D722A
7 Purple #7B3A96
8 Yellow #C7B42E
9 Red    #CB2027


$shapes
# A tibble: 5 x 4
name                         pch character unicode
<chr>                      <int> <chr>     <chr>
  1 WHITE CIRCLE                   1 ○         U+25CB
2 WHITE SQUARE                   0 □         U+25A1
3 WHITE UP-POINTING TRIANGLE     2 △         U+25B3
4 PLUS SIGN                      3 +         U+002B
5 MULTIPLICATION X               4 ✕         U+2715





$shapes
# A tibble: 13 x 4
   name                          unicode character    pch
   <chr>                         <chr>   <chr>      <int>
 1 BLACK SQUARE                  U+25A0  ■          -9632
 2 BLACK DIAMOND                 U+25C6  ◆          -9670
 3 BLACK DOWN-POINTING CHARACTER U+25BC  ▼          -9660
 4 BLACK UP-POINTING TRIANGLE    U+25B2  ▲          -9650
 5 BLACK RIGHT-POINTING TRIANGLE U+25B6  ▶          -9654
 6 BLACK LEFT-POINTING TRIANGLE  U+25C0  ◀          -9664
 7 BLACK BOWTIE                  U+29D3  ⧓         -10707
 8 BLACK HOURGLASS               U+29D7  ⧗         -10711
 9 BLACK CIRCLE                  U+25CF  ●          -9679
10 BLACK FOUR POINTED STAR       U+2726  ✦         -10022
11 MULTIPLICATION X              U+2715  ✕         -10005
12 PLUS SIGN                     U+002B  +            -43
13 ASTERISK OPERATOR             U+2217  ∗          -8727

$colors
# A tibble: 12 x 2
   name     value  
   <chr>    <chr>  
 1 Chart 1  #004586
 2 Chart 2  #ff420e
 3 Chart 3  #ffd320
 4 Chart 4  #579d1c
 5 Chart 5  #7e0021
 6 Chart 6  #83caff
 7 Chart 7  #314004
 8 Chart 8  #aecf00
 9 Chart 9  #4b1f6f
10 Chart 10 #ff950e
11 Chart 11 #c5000b
12 Chart 12 #0084d1



ggthemes_data$fivethirtyeight
# A tibble: 6 x 2
  name        value  
  <chr>       <chr>  
1 Dark Gray   #3C3C3C
2 Medium Gray #D2D2D2
3 Light Gray  #F0F0F0
4 Red         #FF2700
5 Blue        #008FD5
6 Green       #77AB43

```

